### 2019-06-21 Writing/draft.tex
Finalised version (to check)

\begin{document}
%Running head
\begin{flushright}s
Version dated: \today
\end{flushright}

@@

\subsection{Effect of character differences on topology}
As expected, there is a significant effect of character difference in the ability to recover the correct topology \hl{(in terms of clades)}.
The character difference metric can be seen as the inverse of character correlation (see Methods above): a high character difference approximates a low level of character correlation and vice versa.
When characters are correlated, one could expect the matrices to convey a strong (but potentially misleading) phylogenetic signal since every character agrees with each other and conversely, when characters are uncorrelated, one could expect them to convey a weaker phylogenetic signal with a high amount of homoplasy.
Intuitively, one would hypothesise that the ``minimised'' character difference scenario would lead to incorrect but consistent trees (\hl{i.e. because the characters are not different, they all support the same topology that might be incorrect}), the ``maximised'' scenario to lead to poorly resolved trees (\hl{i.e. because characters are different, the matrix has a lot of homoplasy leading to badly resolved topologies}) and the ``randomised'' scenario to perform the best at recovering the correct topology (\hl{i.e. a simple bootstrap procedure}). 
\hl{However, throughout our simulation, the ``minimised'' character difference scenario (i.e. increased correlation) tended to result in trees slightly closer to the ``true'' tree and the ``maximised'' character difference scenario (i.e. decreased correlation) led to slightly worst trees (Fig.}
\ref{Fig:RF_results_best}.
\hl{This effect of increasing or reducing character difference did not however appear to affect the taxon placement ($NTS_{Tr}$) for which the confidence intervals overlapped too much to be able to discern clear statistical differences (Fig.}
\ref{Fig:Tr_results_best}).
\hl{However this results needs to be contrasted with the fact that}
the trees generated by the ``minimised'' character difference scenario do not appear better resolved (towards any topology) than the other scenarios (see supplementary material 3, \hl{Figs 9, 10 and 11}).
\hl{Furthermore, it is important to note that on average, fewer characters were duplicated (replaced) in the ``minimised'' matrices compared to both the ``maximised'' and ``randomised'' matrices (supplementary material 3, Figs 4, 5 and 6 - likely due to the fact that replacing only a few highly different characters can drastically decrease the character difference).
However, this change in the amount of replaced characters did not change the way average character differences varied across the three transformed matrices: the character differences were always consistently increased (``maximised''), decreased (``minimised'') and maintained at a normal level (``randomised'') for each replicate (supplementary material 3, Figs 1, 2 and 3).
This suggest that character difference can be decreased with a smaller amount of characters replacements than increasing it.}

\subsubsection{Number of characters and taxa}
Because of the nature of our simulation protocol, one could expect that the effect of character correlation would have increased with the number of characters (i.e. the more characters available, the more characters are modified in each scenario).
Similarly, one could expect the number of taxa to have an effect of the raw ability to recover the ``normal'' topology (i.e. the more taxa, the more likely taxa are misplaced by chance).
\hl{Overall, it is expected that minimising character difference (increasing character correlation) is likely to have a greater effect on recovering the ``correct'' topology since most characters will provide the same phylogenetic signal.
If the ``minimised'' matrix consists of a handful of characters with high consistency with the ``best'' tree, then the tree estimate will be good (for at least part of the tree).
Similarly, the characters in the ``minimised'' matrix are mainly inconsistent with the ``best'' tree then the estimates will be poor.}

Although we measured a significant difference between smaller and larger matrices (\hl{in terms of number of characters, between 100 and 1000 characters - $BC$ $NTS_{RF}=0.914$ and $BC$ $NTS_{Tr}=0.826$}; Tables \ref{Tab_pooledscharacters_test} and \ref{Tab_pooledstaxa_test}),
these differences have to be contrasted with the probability of overlap between the results distributions that are always \hl{very} high between every matrix's size (Bhattacharrya Coefficients $>0.949$ for both the different number of characters and taxa).
This suggests that the overall character difference metric \hl{can be used as a proxy} for character correlation as it is \hl{not directly dependent} on the number of characters analysed.
Regarding the number of taxa, our results suggest that the effect of character correlation on recovering the right topology is independent on the size of the matrix when pooling the data (\hl{i.e. when combining the simulations together}).
Furthermore, using the Normalised Tree Similarity metric ($NTS$) accounts for the fact that topological difference is affected by the sheer number of taxa considered (i.e. we corrected for the expected difference when comparing two random trees with the same number of taxa).

@@

The differences in performance of the Bayesian and parsimony approaches observed here could be due to the inherent mechanisms of each method.
For any given topology $T$ that was obtained from the ``normal'' matrix and a matrix with high homoplasy, both methods will generate scores differently:
(1) in parsimony, the topology will probably be given a bad score (one that implies many changes along the tree) and the optimality criterion (favouring the minimum score) will likely discard the focal topology.
The tree search will thus likely result in a topology island that will not contain the given topology $T$.
(2) in Bayesian inference, the topology will also be given a bad score (i.e. low likelihood) although the high homoplasy can be accommodated in the tree through high evolution rates or/and long branches.
The rate and the branch length being two parameters among others, the score (the likelihood) will change less drastically than for using parsimony.
Furthermore, in Bayesian inference, a reasonable difference in optimality between two topologies (the acceptance) will not necessarily mean that the given topology $T$ will be discarded.
This difference in both mechanisms could explain why, on average, Bayesian inference seems better to recover the ``normal'' topology than maximum parsimony.
\hl{This can be also supported by the fact that Bayesian inference recovered the ``true'' tree topology slightly but consistently better (supplementary materials 3, figures 12, 13, and 14).}

@@

It is important to note that the two other sources of character correlation could also be present in our simulations although they were not explicitly modelled:
(1) evolutionary correlation is implied by simulating the characters based on Birth-Death trees;
and (2) intra-organismal correlation could also be present in the matrices for those characters randomly simulated but sharing similar evolutionary simulation regimes (i.e. creating ``modules'' of characters).
However, the effect of these sources of correlation was out of the scope of this study and would have required \textit{a posteriori} changes to the matrices \hl{(i.e. inferring the topology first and looking at character's correlation based on the observed topology}\citealt{Lande1983,Maddison1990,Pagel1994}).

\subsection{Limitations}
First, simulating evolutionary history is complex.
Not only because the models we're using to infer phylogenies are ever improving \citep[e.g.][]{heath2014fossilized,Wright01072016} but also because generalising morphological evolution across vastly different organisms is probably impossible \citep[see constrasted discussions from][]{GoloboffEmpirical,OReillyEmpirical}.
However, we do not compare the ``maximised'', ``minimised'' and ``randomised'' to the ``true'' tree but rather to the ``normal'' tree.
This allows us to reduce the caveats from our simulations on the effect of character correlation since we only compare the simulation end products to each other (the outputs) rather than to the simulation inputs.
\hl{It is also worth noting that character similarity at the tips does not necessarily reflects identical evolutionary history.
This may be specifically true when simulating characters based on the M$k$ model where the resulting tip states does not necessarily reflects variation of the state along the branches}
\citep[e.g.][]{revell2014ancestral}.
\hl{However, in empirical studies, such state changes along the branches are nearly always empirically unknown (even though they can be estimated by Maximum Likelihood).}

Second, measuring and modifying character correlation is difficult. 
In our simulation protocol we chose to create simulation by duplicating characters in a matrix to maximise or minimise correlation
\hl{(supplementary materials 3, figures 1, 2 and 3).}
In biology, this correlation arises from either intra-organismal or evolutionary mechanisms.
This could lead to correlations between characters to be more present in some parts of the trees that other \citep[e.g. in the case of inapplicable data ][]{BrazeauNA}.
However, because of the number of characters, it is actually complex to actually measure their correlation in a biological sense and is still actively discussed in the literature \citep{Lande1983,Maddison1990,Pagel1994,Pagel2006,goswami2006morphological,goswami2010,goswami2014macroevolutionary,Grabowski2016}.
Additionally, as discussed in the introduction, character correlation can also simply arise by chance due to the discrete coding scheme (i.e. some sets of characters can be highly correlated but effectively describe independent information).
Therefore, we made the choice to simplify our simulations by generating character correlation as a stochastic process rather than a biological one.

@@

It is noteworthy to point that in rather small matrices (25 $\times$ 100), there was no significant difference in terms of recovering the right topology when maximising or randomising the character differences.
Since many discrete morphological matrices are of similar size \citep{guillerme2016assessment} a simple bootstrap re-sampling (i.e. the equivalent of randomising the character differences in our analysis) will be sufficient to obtain a robust topology (\textit{cf.} actively collecting different characters).
In matrices with more taxa, however, the \hl{``minimised''} scenario resulted in better topological recovery than any other scenarios.
Applying this kind of bootstraps that minimised character difference by biasing the random sampling could thus \hl{help understanding which characters generate more homoplasy and which nodes in the tree are conflictual.}

@@

However, in modest size matrices (25 taxa; 100 to 350 characters), the effect of actively choosing to minimise \hl{or maximised} character correlation was not more significant than simply randomising (i.e. bootstrapping) the matrix, suggesting that character correlation is more a problem in large discrete morphological matrices.
For such matrices, minimising the character correlation (resampling characters $<25$\% different) or maximising it ($>75$\%) respectively significantly increased and decreased correct topological recovery compared to randomly resample matrices.

@@

\section{Acknowledgements}
Calculations where done using the Imperial College London Cluster Services (doi: 10.14469/hpc/2232) and the Australian QRIScloud Awoonga cluster services. We thank Alberto Pascual Garcia for input in the design of the simulations protocol, Guillermo Herraiz Yebes for helping with the CD metric proof and Orlin Todorov for assistance with the computations. We also thank the \hl{three anonymous reviewers for there constructive and insightful comments}.

>>>>

\begin{document}
%Running head
\begin{flushright}
Version dated: \today
\end{flushright}

@@

\subsection{Effect of character differences on topology}
As expected, there is a significant effect of character difference in the ability to recover the correct topology (in terms of clades).
The character difference metric can be seen as the inverse of character correlation (see Methods above): a high character difference approximates a low level of character correlation and vice versa.
When characters are correlated, one could expect the matrices to convey a strong (but potentially misleading) phylogenetic signal since every character agrees with each other and conversely, when characters are uncorrelated, one could expect them to convey a weaker phylogenetic signal with a high amount of homoplasy.
Intuitively, one would hypothesise that the ``minimised'' character difference scenario would lead to incorrect but consistent trees (i.e. because the characters are not different, they all support the same topology that might be incorrect), the ``maximised'' scenario to lead to poorly resolved trees (i.e. because characters are different, the matrix has a lot of homoplasy leading to badly resolved topologies) and the ``randomised'' scenario to perform the best at recovering the correct topology (i.e. a simple bootstrap procedure). 
However, throughout our simulation, the ``minimised'' character difference scenario (i.e. increased correlation) tended to result in trees slightly closer to the ``true'' tree and the ``maximised'' character difference scenario (i.e. decreased correlation) led to slightly worst trees (Fig. \ref{Fig:RF_results_best}).
This effect of increasing or reducing character difference did not however appear to affect the taxon placement ($NTS_{Tr}$) for which the confidence intervals overlapped too much to be able to discern clear statistical differences (Fig.\ref{Fig:Tr_results_best}).
However this results needs to be contrasted with the fact that the trees generated by the ``minimised'' character difference scenario do not appear better resolved (towards any topology) than the other scenarios (see supplementary material 3, Figs 9, 10 and 11).
Furthermore, it is important to note that on average, fewer characters were duplicated (replaced) in the ``minimised'' matrices compared to both the ``maximised'' and ``randomised'' matrices (supplementary material 3, Figs 4, 5 and 6 - likely due to the fact that replacing only a few highly different characters can drastically decrease the character difference).
However, this change in the amount of replaced characters did not change the way average character differences varied across the three transformed matrices: the character differences were always consistently increased (``maximised''), decreased (``minimised'') and maintained at a normal level (``randomised'') for each replicate (supplementary material 3, Figs 1, 2 and 3).
This suggest that character difference can be decreased with a smaller amount of characters replacements than increasing it.

\subsubsection{Number of characters and taxa}
Because of the nature of our simulation protocol, one could expect that the effect of character correlation would have increased with the number of characters (i.e. the more characters available, the more characters are modified in each scenario).
Similarly, one could expect the number of taxa to have an effect of the raw ability to recover the ``normal'' topology (i.e. the more taxa, the more likely taxa are misplaced by chance).
Overall, it is expected that minimising character difference (increasing character correlation) is likely to have a greater effect on recovering the ``correct'' topology since most characters will provide the same phylogenetic signal.
If the ``minimised'' matrix consists of a handful of characters with high consistency with the ``best'' tree, then the tree estimate will be good (for at least part of the tree).
Similarly, the characters in the ``minimised'' matrix are mainly inconsistent with the ``best'' tree then the estimates will be poor.

Although we measured a significant difference between smaller and larger matrices (in terms of number of characters, between 100 and 1000 characters - $BC$ $NTS_{RF}=0.914$ and $BC$ $NTS_{Tr}=0.826$; Tables \ref{Tab_pooledscharacters_test} and \ref{Tab_pooledstaxa_test}),
these differences have to be contrasted with the probability of overlap between the results distributions that are always very high between every matrix's size (Bhattacharrya Coefficients $>0.949$ for both the different number of characters and taxa).
This suggests that the overall character difference metric can be used as a proxy for character correlation as it is not directly dependent on the number of characters analysed.
Regarding the number of taxa, our results suggest that the effect of character correlation on recovering the right topology is independent on the size of the matrix when pooling the data (i.e. when combining the simulations together).
Furthermore, using the Normalised Tree Similarity metric ($NTS$) accounts for the fact that topological difference is affected by the sheer number of taxa considered (i.e. we corrected for the expected difference when comparing two random trees with the same number of taxa).

@@

The differences in performance of the Bayesian and parsimony approaches observed here could be due to the inherent mechanisms of each method.
For any given topology $T$ that was obtained from the ``normal'' matrix and a matrix with high homoplasy, both methods will generate scores differently:
(1) in parsimony, the topology will probably be given a bad score (one that implies many changes along the tree) and the optimality criterion (favouring the minimum score) will likely discard the focal topology.
The tree search will thus likely result in a topology island that will not contain the given topology $T$.
(2) in Bayesian inference, the topology will also be given a bad score (i.e. low likelihood) although the high homoplasy can be accommodated in the tree through high evolution rates or/and long branches.
The rate and the branch length being two parameters among others, the score (the likelihood) will change less drastically than for using parsimony.
Furthermore, in Bayesian inference, a reasonable difference in optimality between two topologies (the acceptance) will not necessarily mean that the given topology $T$ will be discarded.
This difference in both mechanisms could explain why, on average, Bayesian inference seems better to recover the ``normal'' topology than maximum parsimony.
This can be also supported by the fact that Bayesian inference recovered the ``true'' tree topology slightly but consistently better (supplementary materials 3, figures 12, 13, and 14).

@@

It is important to note that the two other sources of character correlation could also be present in our simulations although they were not explicitly modelled:
(1) evolutionary correlation is implied by simulating the characters based on Birth-Death trees;
and (2) intra-organismal correlation could also be present in the matrices for those characters randomly simulated but sharing similar evolutionary simulation regimes (i.e. creating ``modules'' of characters).
However, the effect of these sources of correlation was out of the scope of this study and would have required \textit{a posteriori} changes to the matrices (i.e. inferring the topology first and looking at character's correlation based on the observed topology \citealt{Lande1983,Maddison1990,Pagel1994}).

\subsection{Limitations}
First, simulating evolutionary history is complex.
Not only because the models we're using to infer phylogenies are ever improving \citep[e.g.][]{heath2014fossilized,Wright01072016} but also because generalising morphological evolution across vastly different organisms is probably impossible \citep[see constrasted discussions from][]{GoloboffEmpirical,OReillyEmpirical}.
However, we do not compare the ``maximised'', ``minimised'' and ``randomised'' to the ``true'' tree but rather to the ``normal'' tree.
This allows us to reduce the caveats from our simulations on the effect of character correlation since we only compare the simulation end products to each other (the outputs) rather than to the simulation inputs.
It is also worth noting that character similarity at the tips does not necessarily reflects identical evolutionary history.
This may be specifically true when simulating characters based on the M$k$ model where the resulting tip states does not necessarily reflects variation of the state along the branches \citep[e.g.][]{revell2014ancestral}.
However, in empirical studies, such state changes along the branches are nearly always empirically unknown (even though they can be estimated by Maximum Likelihood).

Second, measuring and modifying character correlation is difficult. 
In our simulation protocol we chose to create simulation by duplicating characters in a matrix to maximise or minimise correlation (supplementary materials 3, figures 1, 2 and 3).
In biology, this correlation arises from either intra-organismal or evolutionary mechanisms.
This could lead to correlations between characters to be more present in some parts of the trees that other \citep[e.g. in the case of inapplicable data ][]{BrazeauNA}.
However, because of the number of characters, it is actually complex to actually measure their correlation in a biological sense and is still actively discussed in the literature \citep{Lande1983,Maddison1990,Pagel1994,Pagel2006,goswami2006morphological,goswami2010,goswami2014macroevolutionary,Grabowski2016}.
Additionally, as discussed in the introduction, character correlation can also simply arise by chance due to the discrete coding scheme (i.e. some sets of characters can be highly correlated but effectively describe independent information).
Therefore, we made the choice to simplify our simulations by generating character correlation as a stochastic process rather than a biological one.

@@

It is noteworthy to point that in rather small matrices (25 $\times$ 100), there was no significant difference in terms of recovering the right topology when maximising or randomising the character differences.
Since many discrete morphological matrices are of similar size \citep{guillerme2016assessment} a simple bootstrap re-sampling (i.e. the equivalent of randomising the character differences in our analysis) will be sufficient to obtain a robust topology (\textit{cf.} actively collecting different characters).
In matrices with more taxa, however, the ``minimised'' scenario resulted in better topological recovery than any other scenarios.
Applying this kind of bootstraps that minimised character difference by biasing the random sampling could thus help understanding which characters generate more homoplasy and which nodes in the tree are conflictual.

@@

However, in modest size matrices (25 taxa; 100 to 350 characters), the effect of actively choosing to minimise or maximised character correlation was not more significant than simply randomising (i.e. bootstrapping) the matrix, suggesting that character correlation is more a problem in large discrete morphological matrices.
For such matrices, minimising the character correlation (resampling characters $<25$\% different) or maximising it ($>75$\%) respectively significantly increased and decreased correct topological recovery compared to randomly resample matrices.

@@

\section{Acknowledgements}
Calculations where done using the Imperial College London Cluster Services (doi: 10.14469/hpc/2232) and the Australian QRIScloud Awoonga cluster services. We thank Alberto Pascual Garcia for input in the design of the simulations protocol, Guillermo Herraiz Yebes for helping with the CD metric proof and Orlin Todorov for assistance with the computations. We also thank the three anonymous reviewers for there constructive and insightful comments.
